<<<<<<< HEAD
---
title: "Wild Git Collaboration Practice"
format: 
  html:
    code-fold: show
execute: 
  warning: false
  message: false
---


## STEP 5: No merge conflicts!

```{r partner 1}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a plot of price vs. carat (or some other
### variables of your choice)


```

```{r partner 2}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a subset based on filtering, e.g., 
### size greater than 1 carat or cut is "Ideal"

library(ggplot2)
library(tidyverse)
data = ggplot2::diamonds

premium = data |>
  mutate(cut=as.character(cut)) |>
  filter(cut == "Premium") |>
  mutate(cut=as.factor(cut))
```

## STEP 7: Uh oh, merge conflicts!

```{r break-it-1}
### Both partners - delete this comment, then write some code here
### to plot, summarize, calculate something simple using the diamonds
### dataset.


```

## STEP 11: And even more merge conflicts!

```{r break-it-2}
### Both partners - delete this comment, then write some code here
### to plot, summarize, calculate something simple using the diamonds
### dataset.


```

=======
---
title: "Wild Git Collaboration Practice"
format: 
  html:
    code-fold: show
execute: 
  warning: false
  message: false
---

```{r}
library(ggplot2)
library(tidyverse)
```


## STEP 5: No merge conflicts!

```{r partner 1}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a plot of price vs. carat (or some other
### variables of your choice)

diamonds_plot <- ggplot(diamonds, aes(x = price, y = depth))+
  geom_line()+
  facet_wrap(~clarity)

diamonds_plot

```

```{r partner 2}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a subset based on filtering, e.g., 
### size greater than 1 carat or cut is "Ideal"



```

## STEP 7: Uh oh, merge conflicts!

```{r break-it-1}
depth_plot <- ggplot(diamonds, aes(x = price, y = depth), color = color)+
  geom_line()

depth_plot
```

## STEP 11: And even more merge conflicts!

```{r break-it-2}
table_plot <- ggplot(diamonds, aes(x = price, y = table), color = color)+
  geom_line()+
  facet_wrap(~color)

table_plot
```

>>>>>>> d9164caa0ee52c3677eeb12bdfe0741d9d5f01cc
